\documentclass{article}

\title{Your Paper Title}
\author{Dolev Dublon,}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
Your introduction text here.

\section{Methodology}
Your methodology text here.

\section{Results}
Your results text here.

\section{Conclusion}
Your conclusion text here.



\section{Introduction}

In the realm of advanced mathematical research, synthesizing and presenting complex ideas clearly and coherently is as crucial as the research itself. This course culminates in such an exercise: creating a short survey that delves into the intricacies of pre-selected topics, with a focus on the Generalisations of the Johnson-Lindenstrauss embedding lemma and the Invertibility of random matrices.

The essence of this assignment is not in reproducing proofs from the chosen articles, but in weaving a narrative that portrays the development, interrelations, and significance of the results within these papers. This narrative should unfold chronologically, providing a backdrop for each result and placing it within the larger tapestry of mathematical research. It should illuminate how each result builds upon or deviates from previous studies, offering insights into the evolution of thought and technique in these specific areas.

A crucial aspect of this survey is to elucidate the importance and the intuition underlying the results. Why do these findings matter? What broader implications do they hold? What conceptual underpinnings drive these results? Addressing these questions will not only deepen the subject matter understanding but also provide a solid foundation for those venturing further into these topics.

Moreover, the survey should employ examples or simple constructions that illustrate these results. These examples are pivotal tools that bridge the gap between abstract theory and tangible understanding. They serve as waypoints in the journey through a dense forest of formulas and theories, offering respite and clarity.

The overarching goal is to produce a report that conveys the 'big picture' of the topics at hand with precision and depth, enabling a reasonably informed reader to delve into the technicalities with confidence. This account should stand as a testament to the ability to distill complex ideas into an accessible format, reflecting a masterful grasp of both the subject matter and the art of communication.


\end{document}

